---
title: "Exercise Bootstrap"
output: html_notebook
---

In this exercise I will implement Exercise 3 of the bootstrap chapter in the Computational Statistics class by Prof. Liebl at Uni Bonn.

We have derived the classic confidence interval as 
\(P=\bar{X}_n - z_{\frac{\alpha}{2}}*\frac{\sigma}{\sqrt{n}}\seq \mu \leq \bar{X}_n + z_{\frac{\alpha}{2}}*\frac{\sigma}{\sqrt{n}}\\)

Outline:
1. Draw random sample from the corresponding distribution, 
2. Estimate confidence interval,
3. Check if true \mu is in CI,
4. Repeat m-many times in Monte Carlo Simulation 

```{r}
knitr::opts_chunk$set(echo = FALSE)

mu <- 1
m <- 10000
n <- 20
mu_cover <- matrix(NA, nrow=m, ncol=1)
contains_mu <- function(lower,upper,mu=1) {
  if (lower <= mu && upper >= mu)
    {return(1)
    } else{return(0)}
}

for(b in 1:m){
  sample <- rnorm(n,mean=1,sd=2)
  lower_bound <- mean(sample)+qnorm(0.025)*sd(sample)/sqrt(n)
  upper_bound <- mean(sample)+qnorm(0.975)*sd(sample)/sqrt(n)
  mu_cover[b,1] <- contains_mu(lower_bound, upper_bound,mu=1)
}
print(mean(mu_cover))
```
```{r}

mean(mu_cover)
```


I switched to classical R for the rest of the exercise.